### 2010-06-29 trunk/paper/IIWAS2010/content/abstract.tex
After Monday's meeting
latest stuff

The Morpheus question answering system uses deep web search to answer user queries. Queries are represented by a semi-structured format that contains query terms and referenced classes within a specific ontology. Morpheus answers questions by using methods stored in prior successful searches answering similar queries. We rank stored methods based on a similarity measure defined on assigned classes of queries. This measure depends on class heterarchy in a realm-based ontology and the associated text corpora. Finally, we revisit the prior search pathways of the stored searches to construct possible answers. The realm-based ontologies are created using the Wikipedia pages, associated categories, and the synset heterarchy of WordNet. This paper describes the entire process with emphasis on the matching of user queries to stored answering methods. The paper also discusses methods to improve generation of an ontology and the associated corpora using methods such as document categorization.

>>>>

The Morpheus question answering system uses deep web search to answer user queries. Queries are represented by a semi-structured format that contains query terms and referenced classes within a specific ontology. Morpheus answers questions by using methods stored in prior successful searches answering similar queries. We rank stored methods based on a similarity quasi-metric defined on assigned classes of queries. Similarity depends on the class heterarchy in an ontology and its associated text corpora. Finally, we revisit the prior search pathways of the stored searches to construct possible answers. The realm-based ontologies are created using Wikipedia pages, associated categories, and the synset heterarchy of WordNet. This paper describes the entire process with emphasis on the matching of user queries to stored answering methods.

### 2010-06-29 trunk/paper/IIWAS2010/content/related_work.tex
latest stuff

\subsection{Ontology generators}

An ontology formally models real world \textit{concepts} and their
relationships. A concept or class in an ontology gives us an abstract and
simplified view of the world\cite{Gruber1993} in a machine-readable and
language-independent format. The relationships and attributes of an
ontological concept are defined using \textit{properties} and \textit{property
restrictions}. An ontology definition contains all of
these: classes, properties, and restrictions. A class in an ontology can have
multiple \textit{super classes} and \textit{sub-classes}. Finally, a
\textit{knowledge base} represents an ontology together with 
instances of its classes.

The DBpedia\footnote{http://dbpedia.org} project is based on extracting
semantic information from the Wikipedia and making it available on the
Web. Wikipedia semantics includes info-box templates, categorization
information, images, Geo-coordinates, links to external Web pages,
disambiguation pages, and redirects between pages in Wiki markup form
\cite{Auer07dbpedia:a, Bizer2009}.

The extraction procedure is as follows: Wikipedia categories are represented
using skos:concepts and category relations are represented using skos:broader
\cite{Auer07dbpedia:a, Bizer2009}. In fact, DBpedia does not define any new
relations between the Wikipedia categories. The Wikipedia categories are
extracted directly from Wikipedia pages and there is no quality check on the
resultant ontology. Similarly, DBpedia uses the info-box attributes and values
as the ontological relations and its ranges.

YAGO is a semi-automatically constructed ontology from Wikipedia and
WordNet\cite{Suchanek2009phd}. The YAGO ontology uses an automated process to
extract information from Wikipedia pages, info-boxes, and categories and to
combine this information with the WordNet\footnote{http://wordnet.princeton.edu}
synsets heterarchy. Since Wikipedia contains more individuals in the form of
Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles
are used as the YAGO ontology individuals. YAGO concentrates mainly on the
fields of people, cities, events, and movies\cite{Suchanek2009phd}.

In addition, YAGO uses Wikipedia categories as its ontology classes. The
ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym}
relations of the WordNet synsets. YAGO uses only the nouns from WordNet and
ignores the WordNet verbs and adjectives. The connection between a WordNet
synset and a Wikipedia category is achieved by parsing the category names and
matching the parsed category components with the WordNet
synsets\cite{Suchanek2009phd}. Those Wikipedia categories having no WordNet
match are ignored in the YAGO ontology.

Moreover, YAGO type extraction is mainly based on the assumption that
each Wikipedia page has at least one tagged category, and the assigned Wikipedia
categories are relevant to that Wikipedia page. The Wikipedia page category
assignments are subjectively assigned by human editors and some Wiki pages are
unassigned i.e., they have no category. In addition, we cannot completely rely
on the relevance of these assigned Wikipedia page categories.

\subsection{NLP Interfaces}

>>>>

The earliest question answering systems such as BASEBALL \cite{Green1961} and Lunar \cite{woods1973} had \emph{closed domains} and \emph{closed corpora}, that is, they supported finitely many questions on copora containing a fixed set of documents.
Morpheus uses the web as its dynamic, open corpus and examines deep web sources 
to answer questions.

Several community QA systems have been developed, such as Yahoo! Answers \cite{yahooanswers2008}. These sites enlist a community of users to answer questions posed by other users.  This idea has led to socially integrated QA systems such as Aardvark \cite{vark2010}. In addition to having questions answered by users, Aardvark can contact potential question answerers through media beyond webpages (e.g. instant messages, mobile phones).  This allows for faster responses to questions.  Morpheus relies on both its user interface and previous similar questions answered by a community of users to give a fast reliable answer.

\subsection{Ontology generators} 
\label{sec:ontology_generators}

% This section needs to be reworkd. It should be about 1 paragraph. It should define
% what these (ontology, dbpedia, wordnet) mean to morpheus
% What rigors boone invest to my pyramids? <<-- randomly generated

%An ontology formally models real world \textit{concepts} and theirrelationships. A concept or class in an ontology gives us an abstract and simplified view of the world\cite{Gruber1993} in a machine-readable and language-independent format. The relationships and attributes of an ontological concept are defined using \textit{properties} and \textit{property restrictions}. An ontology definition contains all of these: classes, properties, and restrictions. A class in an ontology can have multiple \textit{super classes} and \textit{sub-classes}. Finally, a \textit{knowledge base} represents an ontology together with instances of its classes.

%% use dbpedia instead of wikipedia here

The DBpedia\footnote{http://dbpedia.org} project is based on extracting  semantic information from the Wikipedia and making it available on the Web.  Wikipedia semantics includes info-box templates, categorization information,  images, Geo-coordinates, links to external Web pages, disambiguation pages,  and redirects between pages in Wiki markup form \cite{Bizer2009}.  DBpedia represents the Wikipedia categories using skos:concepts and category relations using skos:broader \cite{Bizer2009}. In fact,  DBpedia does not define any new relations between the Wikipedia categories.  The Wikipedia categories are extracted directly from Wikipedia pages, and there  is no quality check on the resultant ontology. Similarly, additional ontological relations in DBpedia are generated from the info-box attributes and their values.

YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy\cite {Suchanek2009phd}. YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes. The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets. YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives. The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}. Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.

However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page. The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages are unassigned i.e., they have no category. In addition, we cannot fully rely on the relevance of these assigned Wikipedia page categories. In addition, YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.
